### 2025-08-14 paper/paper.tex
latex stuff

    \begin{        Initial vector is [1 2 3 4 ... mod 7] (Double check)
        Initial vector is used to align the vectors but it kind of doesn't work
section}{Singular Value Decomposition and Random Dot Product Graphs}
        SVD Calculated with XXX Arpack XXX Julia
        Each system has 2 singular values
        L and R are related by [1 0; 0 -1] as the network is not directed (IE the matrix is symetrical) 
        We only model L and transform it for analysis
        Reconstruct the RDPG L*(L*transform)'
    \end{section}

@@

    \begin{section}{Reconstructing the Temporal Network}
        $u$ is the first row of the matrix $\hat L$. By taking $u\hat R'$, this is equivalent to finding $\hat A = \hat L \hat R'$ and looking at $\hat A_{1\cdot}$; to recover a final prediction of the edges of $u$, we take:
        \begin{align}
            q &= u \hat R'
        \end{align}
        This gives a vector $q$ of probabilities of connections between the target node and the rest of the network. As the results can be interpreted as a probability, the most likely graph is given by setting any entry with a value of $0.5$ or higher to one (predict that the edge exists), and setting any entry with a value of less than $0.5$ to zero (predict that an edge does not exist). However, this may not provide the best fit in terms of the accuracy of edges, and techniques to find the best threshold exist (for more information see \Citeauthor{strydomEtAl}\cite{strydomEtAl})
    \end{section}
\end{chapter}

>>>>

    \begin{section}{Singular Value Decomposition and Random Dot Product Graphs}
        SVD Calculated with XXX Arpack XXX Julia
        Each system has 2 singular values
        Aligning The L and R matrices is important (The SVDs can each be fliped)
        We use an initial vector to ensure that the first eigenvector is oriented the same for each time step
        Then calculate a transformation for the subsequent eigenvectors, which is used for training loss and prediction.
        L and R are related by [1 0; 0 -1] as the network is not directed (IE the matrix is symetrical) 
        We only model L and transform it for analysis
        Reconstruct the RDPG L*(L*transform)'
    \end{section}

@@

    \begin{section}{Reconstructing the Temporal Network}
        XXX Is this necessary XXX

        $u$ is the first row of the matrix $\hat L$. By taking $u\hat R'$, this is equivalent to finding $\hat A = \hat L \hat R'$ and looking at $\hat A_{1\cdot}$; to recover a final prediction of the edges of $u$, we take:
        \begin{align}
            q &= u \hat R'
        \end{align}
        This gives a vector $q$ of probabilities of connections between the target node and the rest of the network. As the results can be interpreted as a probability, the most likely graph is given by setting any entry with a value of $0.5$ or higher to one (predict that the edge exists), and setting any entry with a value of less than $0.5$ to zero (predict that an edge does not exist). However, this may not provide the best fit in terms of the accuracy of edges, and techniques to find the best threshold exist (for more information see \Citeauthor{strydomEtAl}\cite{strydomEtAl})
    \end{section}
\end{chapter}
